Activities

### 2025-11-26 activities.qmd
removed 2nd upcoming (251126GH)

* Invited talk at the [CFE-CMStatistics 2025](https://www.cmstatistics.org/CFECMStatistics2025) (19th International Joint Conference on Computational and Financial Econometrics and Computational and Methodological Statistics) in London, UK, 13-15 Dec 2025. 
Topic of the session: Researcher degrees of freedom, flexible modeling and interpretability. 
Speaker: Theresa Ullmann. 
Topic of the talk: Comparing methods for flexible estimation of non-linear associations: The importance of suitable performance measures (project TG2-P8).

@@

* Invited session at the [ROeS 2025](https://roes2025.at/index.html) (Conference of the Austro-Swiss Region of the International Biometric Society) in Graz, A, 14-18 Sep 2025. Topic of the session: Contrasting Bayesian and frequentist model building for descriptive research questions - a paired-design experiment of STRATOS-TG2. 
Invited speaker: <a href="/assets/Mariana_slides_Roes_2025.pdf" target="_blank" rel="noopener noreferrer">Mariana Nold</a>. 
Further speakers for TG2: <a href="/assets/20250902_Kammer.pdf" target="_blank" rel="noopener noreferrer">Michael Kammer</a>, 
<a href="/assets/Aliaksandr_slides_Roes_2025.pdf" target="_blank" rel="noopener noreferrer">Aliaksandr Hubin</a>, 
<a href="/assets/2025-09 Roes Heinze.pdf" target="_blank" rel="noopener noreferrer">Georg Heinze</a>.

@@

* Invited talk at the [ROeS 2025](https://roes2025.at/index.html) (Conference of the Austro-Swiss Region of the International Biometric Society) in Graz, A, 14-18 Sep 2025. Topic of the session: Towards best practices in medical statistics: The need to implement innovative scientific solutions. Speaker: Theresa Ullmann. Topic of the talk: [Neutral Comparisons Of Statistical Methods: Opportunities, Challenges, And Common Issues](assets/Slides ROeS Ullmann.pdf) (Includes as an example TG2-P11, Simulation study on variable selection)

* Invited session at 70th Annual Meeting of the German Society for Medical Informatics, Biometrics and Epidemiology (Deutsche Gesellschaft für Medizinische Informatik, Biometrie und Epidemiologie e. V., GMDS) in Jena, Germany, 7-11 Sep 2025. Speaker for TG2: Gregor Buch. Topic of the talk: STRATOS Topic Group 2 – Selection of variables and functional forms in multivariable analysis: Results from a review of Covid-19 prognostic models. [Slides](assets/Covid-Modeling-Review_Talk_GMDS2025.pdf)

* Minisymposium at the International Society of Clinical Biostatistics (ISCB) conference in Basel, CH, 28 Aug 2025. Topic of the session: Statistical Research needs to improve – on the important roles of simulation studies and guidance for analysis. Speakers (among others): Georg Heinze, Willi Sauerbrei, Michal Abrahamowicz. [Find out more](https://iscb2025.info/mini-symposia.html#mini-symposium-3-statistical-research-needs-to-improve-on-the-important-roles-of-simulation-studies-and-guidance-for-analysis)

* Topic-contributed paper session at Joint Statistical Meeting (JSM), 6 Aug 2025. Speaker for TG2: Marc Henrion. Topic of the talk: STRATOS Topic Group 2 – Selection of variables and functional forms in multivariable analysis: Results from a review of Covid-19 prognostic models.[Find out more](https://ww2.amstat.org/meetings/jsm/2025/)

@@

* summer activities completed! we are preparing for 2026...

>>>>

* Invited talk at the [CFE-CMStatistics 2025](https://www.cmstatistics.org/CFECMStatistics2025) (19th International Joint Conference on Computational and Financial Econometrics and Computational and Methodological Statistics) in London, UK, 13-15 Dec 2025. 
  * Topic of the session: Researcher degrees of freedom, flexible modeling and interpretability. 
  * Speaker: Theresa Ullmann. 
  * Topic of the talk: Comparing methods for flexible estimation of non-linear associations: The importance of suitable performance measures (project TG2-P8).

@@

* Invited session at the [ROeS 2025](https://roes2025.at/index.html) (Conference of the Austro-Swiss Region of the International Biometric Society) in Graz, A, 14-18 Sep 2025. 
  * Topic of the session: Contrasting Bayesian and frequentist model building for descriptive research questions - a paired-design experiment of STRATOS-TG2. 
  * Invited speaker: Mariana Nold <a href="/assets/Mariana_slides_Roes_2025.pdf" target="_blank" rel="noopener noreferrer">Slides</a>. 
  * Further speakers for TG2: 
    * Michael Kammer <a href="/assets/20250902_Kammer.pdf" target="_blank" rel="noopener noreferrer">Slides</a>, 
    * Aliaksandr Hubin 
<a href="/assets/Aliaksandr_slides_Roes_2025.pdf" target="_blank" rel="noopener noreferrer">Slides</a>, 
    * Georg Heinze <a href="/assets/2025-09 Roes Heinze.pdf" target="_blank" rel="noopener noreferrer">Slides</a>.

@@

* Invited talk at the [ROeS 2025](https://roes2025.at/index.html) (Conference of the Austro-Swiss Region of the International Biometric Society) in Graz, A, 14-18 Sep 2025. 
  * Topic of the session: Towards best practices in medical statistics: The need to implement innovative scientific solutions. 
  * Speaker: Theresa Ullmann. 
  * Topic of the talk: [Neutral Comparisons Of Statistical Methods: Opportunities, Challenges, And Common Issues](assets/Slides ROeS Ullmann.pdf) (Includes as an example TG2-P11, Simulation study on variable selection)

* Invited session at 70th Annual Meeting of the German Society for Medical Informatics, Biometrics and Epidemiology (Deutsche Gesellschaft für Medizinische Informatik, Biometrie und Epidemiologie e. V., GMDS) in Jena, Germany, 7-11 Sep 2025. 
  * Speaker for TG2: Gregor Buch. 
  * Topic of the talk: STRATOS Topic Group 2 – Selection of variables and functional forms in multivariable analysis: Results from a review of Covid-19 prognostic models. [Slides](assets/Covid-Modeling-Review_Talk_GMDS2025.pdf)

* Minisymposium at the International Society of Clinical Biostatistics (ISCB) conference in Basel, CH, 28 Aug 2025. 
  * Topic of the session: Statistical Research needs to improve – on the important roles of simulation studies and guidance for analysis. 
  * Speakers (among others): Georg Heinze, Willi Sauerbrei, Michal Abrahamowicz. [Find out more](https://iscb2025.info/mini-symposia.html#mini-symposium-3-statistical-research-needs-to-improve-on-the-important-roles-of-simulation-studies-and-guidance-for-analysis)

* Topic-contributed paper session at Joint Statistical Meeting (JSM), 6 Aug 2025. Speaker for TG2: Marc Henrion. 
  * Topic of the talk: STRATOS Topic Group 2 – Selection of variables and functional forms in multivariable analysis: Results from a review of Covid-19 prognostic models.[Find out more](https://ww2.amstat.org/meetings/jsm/2025/)

@@
